### 2020-04-01 manuscript/bef_stability/manuscript.Rmd
Add table indir + modify troph group effect

Determining the shape of the relationship between species diversity and ecosystem
functioning has been a central research topic in ecology
[@may_will_1972, @hector_plant_1999, @loreau_biodiversity_2001, @hooper_effects_2005, @duffy_why_2009, @isbell_forest_quantifying_2018].
Current biodiversity losses
in all ecosystems challenge scientists to understand how ecosystems will be
affected in turn. Studies in Bioversity-Ecosystem Functioning (BEF) usually
quantify species diversity as species richness (i.e number of species) while
ecosystem functioning is quantified as total biomass, productivity (biomass
produced by unit of time) or stability which is quantified in more diverse ways
such as the variability of species abundance, the resilience to perturbation, or
resistance to perturbation [@donohue_navigating_2016].

---
#- Diversity - stability and diversity - biomass / productivity
  #- well studied: both experimentally, empirically and theoretically
  #- mecanisms:
    #- stability: insurance (asynchrony),
    #- diversity: overyielding (complementarity)
  #- key papers: [@tilman_biodiversity_2006, @loreau_species_2008,
    #@thibaut_understanding_2013, @may_will_1972]
  #- BUT: less vertical diversity, trophic communities
---

Species richness has been reported to increase productivity in grasslands
[@grace_integrative_2016], but complex links between between species richness,
environment, productivity and total biomass showed that species richness
decrease total biomass [@grace_integrative_2016] contrary to previous
assessment [@hector_plant_1999, @tilman_biodiversity_2014] because of
competition for light between plants [@grace_integrative_2016]. Complementarity
between species in resource exploitation [@cardinale_species_2002] leading to
overyielding (CHECK) has been proposed to explain positive relationship between
productivity and species richness, while species richness effect can also rise
from the statistical probability to end up with a highly productive species
. The relationship between species richness and stability is even more complex
partly because of the inherent multidimensionality of stability
[@donohue_dimensionality_2013, @donohue_navigating_2016] and because of the
different metrics of stability privileged in theoretical (stability of local
equilibrium, robustness to primary extinction) and empirical work (variability
of abundance or biomass through time). @may_will_1972 stimulated a lot of
debate and fecund research, showing that species richness, probability of
interacting and average interaction strength destabilizes communities in which
species interact randomly. Empirically, consistent works showed that species
richness increased community stability in grasslands
[@tilman_biodiversity_2006], mesocosms [@pennekamp_biodiversity_2018] and
vertebrates [@olivier_independent_nodate, @franssen_annual_2011]. Two
components can explain variation of community stability, (1) individual species
stability and (2) the species synchrony [@loreau_species_2008, @thibaut_understanding_2013].
Positive [@tilman_biodiversity_2006], neutral
[@jiang_different_2009, @olivier_independent_nodate] and negative
[@franssen_annual_2011, @olivier_independent_nodate] relationships between
species stability and species richness have been found. On the other side,
studies consistently found that species richness decreased synchrony between
species [@loreau_species_2008, @thibaut_understanding_2013, @bluthgen_land_2016; @olivier_independent_nodate]. However, as far as we know,
less studies have reported empirical assessment of stability-richness
relationship in trophic network [but see @thebault_stability_2010].

@@

# Compute stability, network metrics, etc with ;he new datasets
#debug(summarise_network_over_time)
##myload(network_metrics, dir = mypath("data", "classes"))
#network_metrics %>%
  #left_join(op_analysis, by = "opcod") %>%
  #select(opcod, station, composition) %>%
  #unnest(composition) %>%
  #group_by(station, troph_group) %>%
  #summarise(richness_tot = length(unique(species)))
com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb)
# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]],
  hab_press = habitat_pressure,
  sync = com_data[["sync_std"]],
  nmds = NULL,
  basin = st_basin
  )

@@

```{r get-data, cache = FALSE}
library(nlme)
library(piecewiseSEM)
library(lme4)
ctrl <- lmeControl(opt='optim')
ctrl_lmer <- lmerControl(optCtrl = list(method = 'optimx'))
```

@@

# get coeff
coef_div <- map(list(stab = stab_div_mod, bm = bm_div_mod), fixed.effects)
```

```{r mod-div-troph, fig.show = "hide"}
stab_troph_mod <- lmer(data = stab_div_troph,
  formula = log_stab_std ~ log_rich_tot_std + troph_group + log_rich_tot_std:troph_group + (1 | basin)
  #control = ctrl
)
stab_troph_boot <- bootMer(stab_troph_mod, mySumm2, nsim = 200)
stab_troph_ci <- confint(stab_troph_boot)

stab_troph_colin <- car::vif(stab_troph_mod)
stab_troph_sum <- piecewiseSEM::rsquared(stab_troph_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred_troph_mod <- ggpredict(stab_troph_mod, terms = c("log_rich_tot_std", "troph_group"), type = "fe")
#plot(pred_troph_mod, add.data = TRUE)
stab_troph_pred <- pred_troph_mod %>%
  as_tibble() %>%
  rename(
    log_stab_std = predicted,
    log_rich_tot_std = x,
    troph_group = group
  )

# Productivity and troph group

bm_troph_mod <- lmer(data = na.omit(stab_div_troph),
  #fixed = log_bm ~ log_rich_tot * troph_group,
  formula = log_bm_std ~ log_rich_tot_std + troph_group + log_rich_tot_std:troph_group + (1 | basin)
  #random = ~ 1 + log_rich_tot * troph_group | basin,
  #control = ctrl 
)
bm_troph_boot <- bootMer(bm_troph_mod, mySumm2, nsim = 100)
bm_troph_ci <- confint(bm_troph_boot)

bm_troph_sum <- piecewiseSEM::rsquared(bm_troph_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred_troph_mod <- ggpredict(bm_troph_mod, terms = c("log_rich_tot_std", "troph_group"), type = "fe")
#plot(pred_troph_mod, add.data = TRUE)
bm_troph_pred <- pred_troph_mod %>%
  as_tibble() %>%
  rename(
    log_bm_std = predicted,
    log_rich_tot_std = x,
    troph_group = group
  )

# get coeff
coef_troph <- map(list(stab = stab_troph_mod, bm = bm_troph_mod), fixed.effects)
```

@@

library(ggraph)
p_stab_sem_rich <- ggpiecewisesem(stab_sem_rich)
p_bm_sem_rich <- ggpiecewisesem(bm_sem_rich)

library(DiagrammeR)

p_format <- "png"
p_width <- 700*2
p_height <- 900*2

stab_sem_path <- mypath("manuscript", "bef_stability",
  paste0("stab_sem.", p_format))
bm_sem_path <- mypath("manuscript", "bef_stability",
  paste0("bm_sem.", p_format))

graph_stab_sem <- build_diag_from_sem(
  stab_sem_rich, 
  p_val_thd = 0.05,
  env_x_pos_range = c(from = 0, to = 7.5),
  env_y_pos = 0,
  env_y_sep = 1.5,
  order_env_node = c("RC4", "log_RC3", "RC5", "log_RC1", "log_RC2")  
)
graph_stab_sem %<>%
  add_global_graph_attrs(
    attr = "splines",
    value = "ortho", #spline
    attr_type = "graph")
render_graph(graph_stab_sem)
export_graph(graph = graph_stab_sem, file_type = p_format,
  file_name = stab_sem_path,
  height = p_height - p_height*30/100,
  width = p_width
)
#source(mypath("R", "plot_methods.R")) 
graph_bm_sem <- build_diag_from_sem(
  bm_sem_rich, 
  p_val_thd = 0.05,
  env_x_pos_range = c(from = 0, to = 7.5),
  env_y_pos = 0,
  env_y_sep = 1.5,
  order_env_node = c("RC4", "log_RC3", "RC5", "log_RC1", "log_RC2")  
)
graph_bm_sem %<>%
  add_global_graph_attrs(
    attr = "splines",
    value = "ortho", #spline
    attr_type = "graph")
render_graph(graph_bm_sem)
export_graph(graph = graph_bm_sem, file_type = p_format,
  file_name = bm_sem_path,
  height = p_height - p_height*45/100,
  width = p_width 
)

library(magick)
library(rsvg)
img_stab_sem <- stab_sem_path %>%
  image_read()
p_stab_sem_rich <- ggdraw() +
  draw_image(img_stab_sem)
img_bm_sem <- bm_sem_path %>%
  image_read()
p_bm_sem_rich <- ggdraw() +
  draw_image(img_bm_sem)
```

@@

```{r get-bm-sem-single-effect}
bm_sem_coef <- filter(coef_bm_sem, P.Value <= 0.05)
get_clean_sem_coef <- function(sem = NULL, resp = NULL, pred = NULL) {
  out <- sem[sem$Response == resp & sem$Predictor == pred, ]$Std.Estimate
  out <- ifelse(length(out) == 0, 0, out)
  round(out, 2)
}

@@

# effect of env on bm 
env_on_bm <- get_env_on_bm(fit = bm_all_params, p_val_thl = 0.05,
  type = "std")
# env on com 
env_on_t_lvl <- get_env_on_com(fit = bm_all_params, p_val_thl = 0.05,
  com = "t_lvl", type = "std")
env_on_ct <- get_env_on_com(fit = bm_all_params,
  p_val_thl = 0.05, com = "ct", type = "std")
env_on_richness <- get_env_on_rich(fit = bm_all_params,
  p_val_thl = 0.05, type = "std")
```

```{r get-bm-tot-effect-rich}
tot_rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
  p_val_thl = 0.05, type = "std")
```

@@

```{r get-sem-tot-effect-env}
all_params <- get_coefficient_piecewisesem(sem = stab_sem_rich, p_val_thl = NULL)
# effect of env on stab

env_on_stab <- get_env_on_stab(fit = all_params, p_val_thl = 0.05,
  type = "std")
# effect of env on sync and cv_sp
env_on_sync <- get_env_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_sync", type = "std")
env_on_cv_sp <- get_env_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_cv_sp", type = "std")
# env on com 
env_on_t_lvl <- get_env_on_com(fit = all_params,
  p_val_thl = 0.05,
  com = "t_lvl", type = "std")
env_on_ct <- get_env_on_com(fit = all_params,
  p_val_thl = 0.05,
  com = "ct", type = "std")
env_on_richness <- get_env_on_rich(fit = all_params,
  p_val_thl = 0.05, type = "std")
```

```{r get-sem-tot-effect-rich}
rich_on_stab <- get_rich_on_stab(fit = all_params,
  p_val_thl = 0.05, type = "std")
rich_on_sync <- get_rich_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_sync", type = "std")
rich_on_cv_sp <- get_rich_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_cv_sp", type = "std")
```

@@

# Right plot
p_stab_div_troph <- stab_div_troph %>%
  ggplot(aes(x = log_rich_tot_std, y = log_stab_std, color = troph_group)) +
  geom_point() +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic group"
  ) +
  ylim(lim_log_stab) +
  xlim(lim_log_rich_tot) +
  geom_line(data = stab_troph_pred) +
  geom_ribbon(data = stab_troph_pred,
    aes(ymin = conf.low, ymax = conf.high, color = NULL, group = troph_group),
    alpha = .2) +
  annotate("text", x = -2.75, y = .75, label = make_label_rsq(rsq = stab_troph_sum),
    parse = TRUE) +
  #scale_x_log10() + scale_y_log10() +
  labs(x = richness_lab, y = stab_lab)

@@

p_bm_div_troph <- stab_div_troph %>%
  ggplot(aes(x = log_rich_tot_std, y = log_bm_std, color = troph_group)) +
  geom_point() +
  ylim(lim_log_bm) +
  xlim(lim_log_rich_tot) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic group"
  ) +
  geom_line(data = bm_troph_pred) +
  geom_ribbon(data = bm_troph_pred,
    aes(ymin = conf.low, ymax = conf.high, color = NULL, group = troph_group),
    alpha = .2) +
  annotate("text", x = -2.75, y = -1.0, label = make_label_rsq(rsq = bm_troph_sum),
    parse = TRUE) +
  labs(x = richness_lab, y = bm_lab)

p_bm <- plot_grid(
  p_bm_div,
  p_bm_div_troph + theme(legend.position = "none"),
  ncol = 2,
  rel_widths = c(.4, .6),
  labels = c("C", "D")
)
```
```{r}
troph_caption <- paste0(
  "The effect of species richness on biomass stability
  (upper panel) and total biomass (bottom panel) for the whole community (left
    panel) and the community splited by trophic group (right panel)."
)

@@

print_coef <- function (vec){
  round(abs(vec)*100)
}
print_ci <- function(.df){
  .df <- round(.df, 3)*100

  paste0("[", .df[["2.5 %"]],";",.df[["97.5 %"]] ,"]")
}
```

```{r print-coef-stab}
# Coefficients
s_co_i <- print_coef(coef_div$stab["(Intercept)"])
s_co_r <- print_coef(coef_div$stab["log_rich_tot_std"])
s_co_t <- print_coef(coef_troph$stab["troph_group3"])
s_co_r_t2 <- print_coef(coef_troph$stab["log_rich_tot_std"])
s_co_r_t3 <- print_coef(coef_troph$stab["log_rich_tot_std"]+coef_troph$stab["log_rich_tot_std:troph_group3"])

@@

```{r tab-coeff-stab}

>>>>

##### BEF
Determining the shape of the relationship between species diversity and ecosystem
functioning has been a central research topic in ecology
[@may_will_1972, @hector_plant_1999, @loreau_biodiversity_2001, @hooper_effects_2005, @duffy_why_2009, @isbell_forest_quantifying_2018].
Current biodiversity losses
in all ecosystems challenge scientists to understand how ecosystems will be
affected in turn. Studies in Bioversity-Ecosystem Functioning (BEF) usually
quantify species diversity as species richness (i.e number of species) while
ecosystem functioning is quantified as total biomass, productivity (biomass
produced by unit of time) or stability which is quantified in more diverse ways
such as the variability of species abundance, the resilience to perturbation, or
resistance to perturbation [@donohue_navigating_2016].

Species richness has been reported to increase productivity in grasslands
[@grace_integrative_2016], but complex links between between species richness,
environment, productivity and total biomass showed that species richness
decrease total biomass [@grace_integrative_2016] contrary to previous
assessment [@hector_plant_1999, @tilman_biodiversity_2014]. Complementarity
between species in resource exploitation [@cardinale_species_2002] leading to
overyielding (CHECK) has been proposed to explain positive relationship between
productivity and species richness, while species richness effect can also rise
from the statistical probability to end up with a highly productive species
. The relationship between species richness and stability is even more complex
partly because of the inherent multidimensionality of stability
[@donohue_dimensionality_2013, @donohue_navigating_2016] and because of the
different metrics of stability privileged in theoretical (stability of local
equilibrium, robustness to primary extinction) and empirical work (variability
of abundance or biomass through time). @may_will_1972 stimulated a lot of
debate and fecund research, showing that species richness, probability of
interacting and average interaction strength destabilizes communities in which
species interact randomly. Empirically, consistent works showed that species
richness increased community stability in grasslands
[@tilman_biodiversity_2006], mesocosms [@pennekamp_biodiversity_2018] and
vertebrates [@olivier_independent_nodate, @franssen_annual_2011]. Two
components can explain variation of community stability, (1) individual species
stability and (2) the species synchrony [@loreau_species_2008, @thibaut_understanding_2013].
Positive [@tilman_biodiversity_2006], neutral
[@jiang_different_2009, @olivier_independent_nodate] and negative
[@franssen_annual_2011, @olivier_independent_nodate] relationships between
species stability and species richness have been found. On the other side,
studies consistently found that species richness decreased synchrony between
species [@loreau_species_2008, @thibaut_understanding_2013, @bluthgen_land_2016; @olivier_independent_nodate]. However, as far as we know,
less studies have reported empirical assessment of stability-richness
relationship in trophic network [but see @thebault_stability_2010].

@@

# Compute stability, network metrics, etc with ;he new datasets
#debug(summarise_network_over_time)
##myload(network_metrics, dir = mypath("data", "classes"))
#network_metrics %>%
  #left_join(op_analysis, by = "opcod") %>%
  #select(opcod, station, composition) %>%
  #unnest(composition) %>%
  #group_by(station, troph_group) %>%
  #summarise(richness_tot = length(unique(species)))
com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb,
 type_network_metrics = "classes" 
)
# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]],
  hab_press = habitat_pressure,
  sync = com_data[["sync_std"]],
  nmds = NULL,
  basin = st_basin
  )

@@

```{r get-data, cache = FALSE}
library(piecewiseSEM)
library(lme4)
library(nlme)

#ctrl <- lmeControl(opt='optim')
ctrl_lmer <- lmerControl(optCtrl = list(method = 'optimx'))
```

@@

# get coeff
coef_div <- map(list(stab = stab_div_mod, bm = bm_div_mod), fixef)
```

```{r mod-div-troph, fig.show = "hide"}
stab_troph_mod <- lmer(data = na.omit(stab_div_troph),
  formula = log_stab_std ~ log_rich_tot_std + troph_group + log_rich_tot_std:troph_group + (1 | basin)
  #control = ctrl
)

stab_troph_mod <- lmer(data = na.omit(stab_div_troph),
  formula = log_stab_std ~  troph_group + (1 | basin)
  #control = ctrl
)

stab_troph_boot <- bootMer(stab_troph_mod, mySumm2, nsim = 100)
stab_troph_ci <- confint(stab_troph_boot)

#stab_troph_colin <- car::vif(stab_troph_mod)
stab_troph_sum <- piecewiseSEM::rsquared(stab_troph_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

#pred_troph_mod <- ggpredict(stab_troph_mod, terms = c("log_rich_tot_std", "troph_group"), type = "fe")
##plot(pred_troph_mod, add.data = TRUE)
#stab_troph_pred <- pred_troph_mod %>%
  #as_tibble() %>%
  #rename(
    #log_stab_std = predicted,
    #log_rich_tot_std = x,
    #troph_group = group
  #)

## Productivity and troph group

#bm_troph_mod <- lmer(data = na.omit(stab_div_troph),
  ##fixed = log_bm ~ log_rich_tot * troph_group,
  #formula = log_bm_std ~ log_rich_tot_std + troph_group + log_rich_tot_std:troph_group + (1 | basin)
  ##random = ~ 1 + log_rich_tot * troph_group | basin,
  ##control = ctrl 
#)
#bm_troph_boot <- bootMer(bm_troph_mod, mySumm2, nsim = 100)
#bm_troph_ci <- confint(bm_troph_boot)

#bm_troph_sum <- piecewiseSEM::rsquared(bm_troph_mod, method = "nagelkerke") %>%
  #mutate_at(vars(Conditional, Marginal), ~round(., 2))

#pred_troph_mod <- ggpredict(bm_troph_mod, terms = c("log_rich_tot_std", "troph_group"), type = "fe")
##plot(pred_troph_mod, add.data = TRUE)
#bm_troph_pred <- pred_troph_mod %>%
  #as_tibble() %>%
  #rename(
    #log_bm_std = predicted,
    #log_rich_tot_std = x,
    #troph_group = group
  #)

## get coeff
#coef_troph <- map(list(stab = stab_troph_mod, bm = bm_troph_mod), fixed.effects)
```
```{r stab-div-troph}
stab_div_by_troph <- compute_stat_troph_rich(
  .data = stab_div_troph,
  resp = "log_stab_std"
)

bm_div_by_troph <- compute_stat_troph_rich(
  .data = stab_div_troph,
  resp = "log_bm_std"
)
troph_perm_test <- map(c(stab = "log_stab_std", bm = "log_bm_std"),
  ~test_troph(.data = stab_div_troph, var = .x)
  )
troph_perm_test$bm$obs
troph_perm_test$stab$obs
troph_perm_test$bm$p_val
troph_perm_test$stab$p_val

@@

library(DiagrammeR)
p_stab_sem_rich <- export_diagram(
  fit = stab_sem_rich,
  file_path = mypath("manuscript", "bef_stability", "stab_sem"),
  format = "png",
  width = 700*2,
  height = 900*2  - 900*2*30/100,
  arrows = "ortho",
  val_thd = 0.05,
  env_x_pos_range = c(from = 0, to = 7.5),
  env_y_pos = 0,
  env_y_sep = 1.5,
  order_env_node = c("RC4", "log_RC3", "RC5", "log_RC1", "log_RC2")
)

p_bm_sem_rich <- export_diagram(
  fit = bm_sem_rich,
  file_path = mypath("manuscript", "bef_stability", "bm_sem"),
  format = "png",
  width = 700*2,
  height = 900*2  - 900*2*45/100,
  arrows = "ortho",
  val_thd = 0.05,
  env_x_pos_range = c(from = 0, to = 7.5),
  env_y_pos = 0,
  env_y_sep = 1.5,
  order_env_node = c("RC4", "log_RC3", "RC5", "log_RC1", "log_RC2")
)
```

@@

```{r get-bm-sem-single-effect}
bm_sem_coef <- filter(coef_bm_sem, P.Value <= 0.05)

@@

# effect of env on bm 
env_on_bm <- get_env_on_bm(fit = bm_all_params, p_val_thl = 0.05,
  type = "std")
# rich on bm 
rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
  p_val_thl = 0.05, type = "std")

tmp_bm_indir_table <- map(list(env_on_bm, rich_on_bm),
  ~as_tibble(c(.x, list(variable = names(.x[[1]]))))
  ) %>%
bind_rows()
```

@@

```{r get-sem-tot-effect-env}
source(mypath("R", "total_sem_effect.R"))
stab_all_params <- get_coefficient_piecewisesem(sem = stab_sem_rich, p_val_thl = NULL)
# effect of env on sync and cv_sp
env_on_sync <- get_env_on_stab_comp(fit = stab_all_params,
  p_val_thl = 0.05,
  stab_comp = "log_sync", type = "std")
env_on_cv_sp <- get_env_on_stab_comp(fit = stab_all_params,
  p_val_thl = 0.05,
  stab_comp = "log_cv_sp", type = "std")
# env on stab via network 
env_on_t_lvl <- get_env_on_com(fit = stab_all_params,
  p_val_thl = 0.05,
  com = "t_lvl", type = "std")
env_on_ct <- get_env_on_com(fit = stab_all_params,
  p_val_thl = 0.05,
  com = "ct", type = "std")
env_on_richness <- get_env_on_rich(fit = stab_all_params,
  p_val_thl = 0.05, type = "std")
```

```{r get-sem-tot-effect-rich}
rich_on_sync <- get_rich_on_stab_comp(fit = stab_all_params,
  p_val_thl = 0.05,
  stab_comp = "log_sync", type = "std")
rich_on_cv_sp <- get_rich_on_stab_comp(fit = stab_all_params,
  p_val_thl = 0.05,
  stab_comp = "log_cv_sp", type = "std")
```

```{r}
# effect of env on stab
env_on_stab <- get_env_on_stab(fit = stab_all_params, p_val_thl = 0.05,
  type = "std")
rich_on_stab <- get_rich_on_stab(fit = stab_all_params,
  p_val_thl = 0.05, type = "std")
com_on_stab <- get_com_on_stab(fit = stab_all_params,
  p_val_thl = 0.05, type = "std")

tmp_stab_indir_table <- map(list(env_on_stab, rich_on_stab, com_on_stab),
  ~as_tibble(c(.x, list(variable = names(.x[[1]]))))

  ) %>%
bind_rows()

@@

# Right plot
p_stab_div_troph <- make_troph_plot(
  .data = stab_div_by_troph,
  resp  = "log_stab_std",
  x_lim = lim_log_rich_tot,
  y_lim = lim_log_stab,
  lab_xy = c(x = richness_lab, y = stab_lab),
  rsq_xy = c(x = -2.75, y = .75) 
  )

@@

p_bm_div_troph <- make_troph_plot(
  .data = bm_div_by_troph,
  resp  = "log_bm_std",
  x_lim = lim_log_rich_tot,
  y_lim = lim_log_bm,
  lab_xy = c(x = richness_lab, y = bm_lab),
  rsq_xy = c(x = -2.75, y = -1.0) 
  )

p_bm <- plot_grid(
  p_bm_div,
  p_bm_div_troph + theme(legend.position = "none"),
  ncol = 2,
  rel_widths = c(.4, .6),
  labels = c("C", "D")
)
```

```{r}
troph_caption <- paste0(
  "The effect of species richness on biomass stability
  (upper panel) and total biomass (bottom panel) for the whole community (left
    panel) and the community splited by trophic group (right panel)."
)
```

@@

```{r print-coef-stab}

# Coefficients
s_co_i <- print_coef(coef_div$stab["(Intercept)"])
s_co_r <- print_coef(coef_div$stab["log_rich_tot_std"])
s_co_t <- print_coef(coef_troph$stab["troph_group3"])
s_co_r_t2 <- print_coef(coef_troph$stab["log_rich_tot_std"])
s_co_r_t3 <- print_coef(coef_troph$stab["log_rich_tot_std"]+coef_troph$stab["log_rich_tot_std:troph_group3"])

@@

#### Indirect effect

```{r indir-tab, fig.cap = "Indirect effect from SEM"}
kable(tmp_stab_indir_table)
kable(tmp_bm_indir_table)
```

### 2020-04-01 report/03-results.Rmd
Add table indir + modify troph group effect

>>>>

## Network properties

### class connectance versus species connectance

```{r}
cl_ct <- temporal_network_metrics_classes %>%
  select(station, connectance_med, nbnode_med) %>%
  rename(cl_ct_med = connectance_med, cl_node_med = nbnode_med)
myload(temporal_network_metrics, dir = mypath("data", "species"))
sp_ct <- temporal_network_metrics %>%
  select(station, connectance_med, nbnode_med) %>%
  rename(sp_ct_med = connectance_med, sp_node_med = nbnode_med)

myload(network_metrics, dir = mypath("data", "classes"))
cl_network_metrics <- network_metrics
myload(network_metrics, dir = mypath("data", "species"))
sp_network_metrics <- network_metrics
sp_net <- sp_network_metrics %>%
  select(opcod, connectance, nbnode) %>%
  rename(sp_ct = connectance, sp_node = nbnode)
cl_net <- cl_network_metrics %>%
  select(opcod, connectance, nbnode) %>%
  rename(cl_ct = connectance, cl_node = nbnode)

net_comp <- sp_net %>% 
  left_join(cl_net, by = "opcod")
```

```{r}
net_comp %>%
  pivot_longer(
        cols = ends_with("ct"),
        names_to = "type",
        names_prefix = "_ct",
        values_to = "ct",
        values_drop_na = TRUE
  ) %>%
  ggplot(aes(x = ct, fill = type)) +
  geom_histogram(position = "identity", alpha = .2) +
  xlab("Connectance")
```

### Weighted average trophic level: class vs species network

```{r}
sp_net <- sp_network_metrics %>%
  select(opcod, w_trph_lvl_avg, nbnode) %>%
  rename(cl_tlvl = w_trph_lvl_avg, cl_node = nbnode)
cl_net <- cl_network_metrics %>%
  select(opcod, w_trph_lvl_avg, nbnode) %>%
  rename(sp_tlvl = w_trph_lvl_avg, sp_node = nbnode)

net_comp <- sp_net %>% 
  left_join(cl_net, by = "opcod")
```

```{r}
net_comp %>%
  pivot_longer(
        cols = ends_with("tlvl"),
        names_to = "type",
        names_prefix = "_tlvl",
        values_to = "tlvl",
        values_drop_na = TRUE
  ) %>%
  ggplot(aes(x = tlvl, fill = type)) +
  geom_histogram(position = "identity", alpha = .2) +
  xlab("Connetlvlance")
```

### 2020-04-01 report/05-stability.Rmd
Add table indir + modify troph group effect

```{r}
myload(nmds, dir = mypath("report"))
lav_data <- compute_sem_dataset(
  com = temporal_community_metrics,
  network = temporal_network_metrics, 
  hab_press = habitat_pressure, 
  sync = synchrony,
  nmds = NULL,
  basin = st_basin 
  )
```

@@

@@

#undebug(build_stab_sem)
corsem <- build_stab_sem(
  evt = c("alt", "width", "DBO_med", "temperature_med"),
  com = c("log_rich", "piel", "c_c", "t_lvl", "beta_bin_c"),
  stab_comp = c("log_sync", "log_cv_sp"),
  stab = c("log_stab"),
  .data = lav_data)

@@

st_basin <- get_basin_station()
myload(nmds, dir = mypath("report"))
myload(network_metrics, dir = mypath("data", "species"))

# Compute stability, network metrics, etc with the new datasets
com_data <- compute_community_temporal_analysis(.op = op_analysis, dest_dir = mypath("data", "species"))
# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]], 
  hab_press = habitat_pressure, 
  sync = com_data[["sync"]],
  nmds = NULL,
  basin = st_basin 
  )

# Compute SEMs
sem <- compute_stab_sem_rich_beta(.data = sem_data,
  random_effect = as.formula("~1|basin"))

ggpiecewisesem(sem)
```

>>>>

@@

st_basin <- get_basin_station()
myload(nmds, dir = mypath("report"))
myload(network_metrics, dir = mypath("data", "species"))
sp_network_metrics <- network_metrics
rm(network_metrics)
myload(network_metrics, dir = mypath("data", "classes"))
cl_network_metrics <- network_metrics
rm(network_metrics)

myload(biomass_ts_sax, dir = mypath("data"))
op_analysis_bbb <- filter(op_analysis, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)

# Compute stability, network metrics, etc with the new datasets
source(mypath("R", "community_analysis.R"))
#debug(compute_community_temporal_analysis)
com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb)
class_tps_net <- summarise_network_over_time(op = op_analysis_bbb,
class_network = cl_network_metrics,
species_network = sp_network_metrics,
metrics = c("connectance", "w_trph_lvl_avg"),
type_metrics = "classes")

# Compute sem dataset 
sem_data <- map(list(sp = com_data[["tps_net"]], cl = class_tps_net),
~compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = .x, 
  hab_press = habitat_pressure, 
  sync = com_data[["sync"]],
  nmds = NULL,
  basin = st_basin 
  )
)

# Compute SEMs
sem <- map(sem_data, ~compute_stab_sem_rich(.data = .x))

library(DiagrammeR)
sem_graph <- map2(
  sem,
  paste0(mypath("manuscript", "bef_stability"), "/", c("species", "class"), "_stab_sem"),
  function(x, path) {

  export_diagram(
    fit = x,
    file_path = path,
    format = "png",
    width = 700*2,
    height = 900*2  - 900*2*30/100,
    arrows = "ortho",
    val_thd = 0.05,
    env_x_pos_range = c(from = 0, to = 7.5),
    env_y_pos = 0,
    env_y_sep = 1.5,
    order_env_node = c("RC4", "log_RC3", "RC5", "log_RC1", "log_RC2")
  )

}
)
```

@@

#undebug(build_stab_sem)
corsem <- build_stab_sem(
  evt = c("alt", "width", "DBO_med", "temperature_med"),
  com = c("log_rich", "piel", "c_c", "t_lvl", "beta_bin_c"),
  stab_comp = c("log_sync", "log_cv_sp"),
  stab = c("log_stab"),
  .data = sem_data)

@@
